\bibitem{self} \textsc{Abou-Chacra R., Thouless D.J.,Anderson P.W} :\ \textit{A selfconsistent theory of localization} Journal of Physics C 6/10 (1973)

\bibitem{hans} \textsc{Bethe H.} :\ \textit{Statistical theory of superlattices.} Proc. Roy. Soc. London A, 150:552–558, 1935.

\bibitem{bowman} \textsc{Bowman D.R., Levin K.} :\ \textit{Spin-glass theory in the Bethe approximation: Insights and problems} Phys. Rev. B 25/5,  (1982).

\bibitem{zullo} \textsc{Carrus C.,Marinari E., Zuliani F.} :\ \textit{Simulations on Bethe lattice spin glass}, unpublished

\bibitem{tersenghi} \textsc{Castellani T., Krzakala F., Ricchi-Tersenghi F.} :\ \textit{Spin glass models with ferromagnetically biased couplings on the Bethe lattice: analytic solutions and numerical simulations} The European Physical Journal B 47/1 (2005)

\bibitem{vulpiani}\textsc{Cencini M.,Cecconi F., Vulpiani A.}:\ \textit{Chaos: from simple models to complex systems}, World Scientific (2010).

\bibitem{instability} \textsc{De Dominicis C.,Mottishaw P.} :\ \textit{On the stability of randomly frustrated systems with finite connectivity},J. Phys. A: Math. Gen. 20 L375 (1987)

\bibitem {shuffle} \textsc{Durstenfeld R.}:\ \textit{Algorithm 235: Random Permutation }, Commun. ACM, 1991).

\bibitem{tempering} \textsc{Earl D.J.,Deem M.W.} :\ \textit{Parallel Tempering: Theory, Applications, and New Perspectives}, a version may be found on arXiv:physics/0508111.

\bibitem{multispin} \textsc{Fang Y., Feng S., Ka-Ming Tam, Zhifeng Yun, Moreno J., Ramanujam J. , Jarrell M.} :\ \textit{Parallel Tempering Simulation of the three-dimensional Edwards-Anderson Model with Compact Asynchronous Multispin Coding on GPU
}, ArXiv e-prints (arXiv:1311.5582 [cond-mat.dis-nn]) .

\bibitem {medina}\textsc{Fernandez J., Medina R.} :\ \textit{Remanence and non-exponential relaxation in an Ising chain with random bonds}, Phys. Rev. B 19/17  (1979).

\bibitem {glass} \textsc{Fisher H., Hertz A.}:\ \textit{Spin glasses }, Cambridge University Press (1991).

\bibitem{life}\textsc{Gardnner M.}\textit{The fantastic combinations of John Conway's new solitaire game "Life"}, Scientific American, 223, 10/1970, pp. 120-123.

\bibitem{guerra} \textsc{Guerra F.}:\ \textit{The Cavity Method In The Mean Field Spin Glass Model. Functional Representations Of Thermodynamic Variables }, preprint

\bibitem {huang} \textsc{Huang K.}:\ \textit{Statistical Mechanics}, italian edition, Zanichelli, 1997

\bibitem{katsu}{Katsura S., Hinawashiro}:\ \textit{Spin-glass phase in the site Ising model}, Journal of Physics. C: Solid State Phys.

\bibitem {kullback} \textsc{Kullback S.}:\ \textit{Information theory and statistics}, Dover publications.

\bibitem{EA} \textsc{Marinari E., Parisi G., Ruiz-Lorenzo J. J.} :\ \textit{On the Phase Structure of the 3D Edwards Anderson Spin Glass
} , Phys. Rev. B. 58, 14852 (1998).

\bibitem{trattatello} \textsc{Marinari E., Parisi G.} :\ \textit{Trattatello di probabilit\'a} , La Sapienza University of Rome (2000)

\bibitem {beyond} \textsc{Mezard M.}:\ \textit{Spin glass theory and beyond}, World Scientific Publishing Company, Incorporated, (1987).

\bibitem {bethe}\textsc{Mezard M., Parisi, G.}:\ \textit{Bethe lattice spin glass revisited} , Eur. Phys. J. B 20, 217 (2001).

\bibitem {mean}\textsc{Mezard M., Parisi, G.}:\ \textit{Mean-Field Theory of Randomly Frustrated Systems with Finite Connectivity},  Europhys. Lett. 3 (1987).

\bibitem {enzo} \textsc{Mezard, M.,}:\ \textit{The cavity method}, Lessons on the cavity method on tree-like structures,
url: http://chimera.roma1.infn.it/GIORGIO60/TALKS/WEDNESDAY/mezard.pdf

\bibitem{wellknown}\textsc{Monasson R.}:\ \textit{Optimization problems and replica symmetry breaking in finite connectivity spin glasses}, Journal of Physics A  31 (1998).

\bibitem{montanari} \textsc{Montanari A.}:\ \textit{Bethe-Peierls approximation: an informal introduction} Lecture, Stat 316 Stochastic Processes on Graphs.

\bibitem {stat} \textsc{Parisi G.}:\ \textit{Statistical field theory},Perseus Books, (1998).

\bibitem {trick} \textsc{Parisi G.}:\ \textit{On the replica approach to spin glasses}, Eur. Phys. J. B (1994).

\bibitem{MCMC}  \textsc{Press W., Teukolsky S., Vetterling W., Flannery B.}:\ \textit{Numerical recipes in C} Cambridge University Press, (1988).

\bibitem {SK}\textsc{Sherrington D., Kirkpatrick S.}:\ \textit{ Infinite ranged model of spin glasses}, Phys. Rev. B 17/11,  (1978).

\bibitem {SK2}\textsc{Sherrington D., Kirkpatrick S.}:\ \textit{ Solvable model of spin glass}, Phys. Rev. Lett. 35/26, (1975).

\bibitem{function} \textsc{Sibani P.,Hertz J. A.} :\ \textit{Parisi function for two spin glass models},
Journal of Physics A 18/8 (1985).

\bibitem{ground}\textsc{Tanaka F., Edwards S.F.}:\ \texit{Analytic theory of the ground state properties of a spin glass. I. Ising spin glass}, Journal of Physics F 10 (1980).

\bibitem{thou}\textsc{Thouless D.J.}:\ \textit{Spin glass on a bethe lattice}, Phys. Rev. Lett. 56, 1082–1085 (1986).


\bibitem{wong}\textsc{Wong K.Y.M., Sherrington D.}:\ \textit{Graph bipartitioning and spin glasses on a random network of fixed finite valence}, Journal of Physics A: Math. Gen. 20 (1987).


\bibitem {critic} \textsc{Zirnbauer M.R.}:\ \textit{Another critique of the replica trick} (1999).
